\section{Methodology}
The processes involved in the development of a directional audio system are broken up into functional deliverables which feed into one another. For this reason a waterfall development model is used to manage the project development life-cycle.
\subsection{Theory}
The theory deliverable involves understanding the various models related to the development of the directional audio system. This includes understanding the principles behind self-demodulating ultrasonic waves and how to implement these principles.
\subsection{Simulation}
The full signal path is simulated from generation/recording, pre-processing of the signals and finally to recreation of the medium within which the ultrasonic waves are produced. The simulations will deliver a flexible environment to test pre-processing ideas and modulation schemes within some simulation limits. Additionally, the simulations aid in selecting an appropriate environment to implement the pre-processing while maintaining a low cost.
\subsection{Design}
This deliverable aims to create designs of the multiple sub-systems required to produce a directional audio system. These subsystems include an ultrasonic transducer array, audio signal pre-processing subsystem, modulation circuit and ultrasonic signal amplifier. Each of these designs may be iterated upon, thus prototyping and testing of these sub-systems during their development is expected.
\subsection{Implementation}
Implementation of the designs needs to be occur often to test the results of any design changes. Thus, the designs are prototyped at first on breadboard and stripboard, allowing for flexible tuning. Upon satisfactory results, the designs may be moved to a full stripboard implementation and finally if circumstances allow it, a PCB design.
\subsection{Testing \& Verification}
The testing and verification of the directional audio system will be done by comparing its acoustic performance with a traditional loudspeaker. Particular test points of interest include the directionality of the speaker and the audible harmonic distortion for pure tone cases.