\begin{abstract}
%The abstract should be a one or two paragraph summary of your paper.  It is meant to sell your paper to interested buyers.
This thesis project aims develop a low cost prototype of a directional audio system based on the self-demodulating phenomenon described by Berktay's far-field solution for ultrasonic pressure waves in air as a medium. The thesis initially outlines relevant theory relating to the directionality of traditional loudspeakers and how higher directionality is achieved with ultrasonic waves.
%A set of objectives including theory and simulation, design, implementation and testing are created to develop the prototype. 
The prior works of the field are mentioned with some discussion of its relevance to the proposed prototype solution. The signal chain is simulated for better understanding of the self-demodulating phenomenon followed by various subsystem designs to implement this signal chain. These designs include mixing, amplification, pre-processing and ultrasonic array designs which are then simulated to verify their operation before their implementation. Each subsystem implementation is tested and compared to simulations with results fed back into the implemented designs to improve their outputs. The directionality and distortion testing methods are then defined and executed for the test setup. The results reveal a significant amount of distortion from the 1st harmonic of the test tone, however; a directional audio beam is achieved featuring self-demodulation. These results are then discussed to further interrogate sources of uncertainty and identify that the modulation technique implemented may be causing added distortion, particularly with the 1st harmonic. The conclusion identifies that the project successfully implemented a low-cost directional speaker and goes on to recommend future improvements for the project.
\end{abstract}
